The function--sheaf dictionary for smooth commutative group schemes over finite fields, with applications over local fields

### 2014-08-23 dictionary.tex
Finished summary of sections

Joseph Bernstein has suggested to us that, although quasicharacter sheaves on $\Gr(\underline{T})$ do not correspond exactly to quasicharacters of $T(K)$, the category $\QC(\Gr_R(\underline{T}))$ is the right one to consider and that $\QC(\Gr(\underline{T})$ may be closely tied to characters of  the pure rational forms of $T$ in the sense of Vogan \cite{vogan:93a} or perhaps the rigid inner twists of Tasho Kaletha. 
A better understanding of 
$\Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Weil{}}$ should provide insight into this suggestion.

@@

Section~\ref{sec:applications} gives applications of quasicharacter sheaves to commutative algebraic groups over local fields.
We begin with a review of N\'eron models and of the Greenberg transform in Section~\ref{ssec:rev_Greenberg}.  We then
define, in Section~\ref{ssec:qc_on_GN}, a quasicharacter sheaf for an algebraic group over a local field to be a quasicharacter
sheaf on the Greenberg transform of the N\'eron model.  In Theorem~\ref{thm:QCXK}, we translate our results from the earlier sections
to give a description of the categories of

@@

\subsection{Quasicharacters of $p$-adic tori}

@@

\subsection{Weil restriction and quasicharacters}\label{sec:wrK}

>>>>

Joseph Bernstein has suggested to us that, although quasicharacter sheaves on $\Gr(\underline{T})$ do not correspond exactly to quasicharacters of $T(K)$, the category $\QC(\Gr(\underline{T}))$ may be closely tied to characters of the pure rational forms of $T$ in the sense of Vogan \cite{vogan:93a} or perhaps the rigid inner twists of Tasho Kaletha. 
A better understanding of 
$\Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Weil{}}$ should provide insight into this suggestion. \todo{rephrase}

@@

Section~\ref{sec:applications} gives applications of quasicharacter sheaves to commutative algebraic groups over local fields.
We begin with a review of N\'eron models and of the Greenberg transform in Section~\ref{ssec:rev_Greenberg}.  We then
define, in Section~\ref{ssec:qc_on_GN}, a quasicharacter sheaf for an algebraic group over a local field to be a quasicharacter
sheaf on the Greenberg transform of the N\'eron model.  In Theorem~\ref{thm:QCXK}, we translate our results from earlier sections
to give a description of the isomorphism classes and automorphism groups
in the category of quasicharacter sheaves on such an algebraic group.
We specialize to $p$-adic tori in Section~\ref{ssec:qc_tori}, and discuss
Weil restriction and base change over local fields in Section~\ref{ssec:wrK}.
Finally, we give a categorical version of a result of Chai and Yu \cite{chai-yu:01a},
relating quasicharacter sheaves for tori over different local fields, even local fields
with different characteristic.

@@

\subsection{Quasicharacters of $p$-adic tori} \label{ssec:qc_tori}

@@

\subsection{Weil restriction and quasicharacters}\label{ssec:wrK}
